Appendix C: Latent Class Growth Analysis

### 2023-01-24 appendix_c.Rmd
revert MGV previous commit

---
title             : "Appendix C: Latent Class Growth Analysis"
shorttitle        : "BEST PRACTICES LATENT CLASS ANALYSIS"
bibliography      : "r-references.bib"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r echo = TRUE, eval = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
ggplot(df_plot, aes(x = scl)) +
  geom_density() +
  facet_wrap(~time) + theme_bw()
```

```{r, eval = run_everything, echo = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
p = ggplot(df_plot, aes(x = scl)) +
  geom_density() +
  facet_wrap(~time) + theme_bw()
ggsave("appendices/plot_dist.png", p, width = 150, height = 120, units = "mm")
```

```{r, echo = FALSE, out.width="50%", eval = pkgdown}
knitr::include_graphics("appendices/plot_dist.png")
```

@@

```{r, eval = FALSE, echo = TRUE}
# Make plot data
df_plot <- do.call(rbind, lapply(c("scl", "log", "sqrt", "qrt", "boxcox"), function(n){
  data.frame(df_scores[c("time", "id")],
             Value = df_scores[[n]],
             Transformation = n)
}))
# Plot
ggplot(df_plot, aes(x = Value, colour = Transformation)) +
  geom_density() +
  facet_wrap(~time) +
  scale_y_sqrt() +
  xlab("scl (rescaled to 0-1)") +
  theme_bw()
```

```{r, eval = run_everything, echo = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
df_scores <- df_plot
# Store original range of SCL
rng_scl <- range(df_scores$scl)
# Log-transform
df_scores$log <- scales::rescale(log(df_scores$scl), to = c(0, 1))
# Square root transform
df_scores$sqrt <- scales::rescale(sqrt(df_scores$scl), to = c(0, 1))
# Cube root transform
df_scores$qrt <- scales::rescale(df_scores$scl^.33, to = c(0, 1))
# Reciprocal transform
df_scores$reciprocal <- scales::rescale(1/df_scores$scl, to = c(0, 1))
# Define function for Box-Cox transformation
bc <- function(x, lambda){
  (((x ^ lambda) - 1) / lambda)
}
# Inverse Box-Cox transformation
invbc <- function(x, lambda){
  ((x*lambda)+1)^(1/lambda)
}
# Box-Cox transform
b <- MASS::boxcox(lm(df_scores$scl ~ 1), plotit = FALSE)
lambda <- b$x[which.max(b$y)]
df_scores$boxcox <- bc(df_scores$scl, lambda)
# Store range of Box-Cox transformed data
rng_bc <- range(df_scores$boxcox)
df_scores$boxcox <- scales::rescale(df_scores$boxcox, to = c(0, 1))
# Rescale SCL
df_scores$scl <- scales::rescale(df_scores$scl, to = c(0, 1))

df_plot <- do.call(rbind, lapply(c("scl", "log", "sqrt", "qrt", "boxcox"), function(n){
  data.frame(df_scores[c("time", "id")],
             Value = df_scores[[n]],
             Transformation = n)
}))
# Plot
p <- ggplot(df_plot, aes(x = Value, colour = Transformation)) +
  geom_density() +
  facet_wrap(~time) +
  scale_y_sqrt() +
  xlab("scl (rescaled to 0-1)") +
  theme_bw()
ggsave("appendices/plot_trans.png", p, width = 150, height = 120, units = "mm")
```

```{r, echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/plot_trans.png")
```

@@

It is important to not that in LCGA, the subgroups will be limited by
the specify growth structure, meaning that LCA will identify distinctive
growth patterns within the intercept, step, and slope growth. For
example, if there is a subgroup that follows a quadratic growth pattern
this models will not be able to identify it.

@@

```{r echo = FALSE, eval = run_everything}
set.seed(27796)
dat[["id"]] <- NULL
res_step <- mx_growth_mixture(
  model =
"i =~ 1*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6
step =~ 0*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6
s =~ 0*scl1 + 0*scl2 + 1*scl3 +2*scl4 +3*scl5 +4*scl6
scl1 ~~ vscl1*scl1
scl2 ~~ vscl2*scl2
scl3 ~~ vscl3*scl3
scl4 ~~ vscl4*scl4
scl5 ~~ vscl5*scl5
scl6 ~~ vscl6*scl6
i ~~ 0*i
step ~~ 0*step
s ~~ 0*s
i ~~ 0*s
i ~~ 0*step
s ~~ 0*step", classes = 1:5,
  data = dat)
# Additional iterations because of
# convergence problems for model 1:
res_step[[1]] <- mxTryHardWideSearch(res_step[[1]], extraTries = 50)
saveRDS(res_step, "appendices/res_step.RData")
fit <- table_fit(res_step)
saveRDS(fit, "appendices/lcga_fit.RData")
```

```{r, echo = FALSE, eval = FALSE}
res_step <- readRDS("appendices/res_step.RData")
```

Note that the first model showed convergence problems, throwing the
error: *The model does not satisfy the first-order optimality conditions
to the required accuracy, and no improved point for the merit function
could be found during the final linesearch.* To address this problem, we
performed additional iterations to\
find a better solution, using `OpenMx::mxTryHardWideSearch()`. This also
illustrates that `tidySEM` mixture models inherit from `OpenMx`'s
`MxModel`, and thus, different `OpenMx` functions can be used to act on
models specified via `tidySEM`.

@@

1.  We do not consider classes with, on average, fewer than 5
    participants per parameter in a class due to potential local
    underidentification
2.  Lower values for information criteria (AIC, BIC, saBIC) indicate
    better fit
3.  Significant Lo-Mendell-Rubin LRT test indicates better fit for $k$
    vs $k-1$ classes
4.  We do not consider solutions with entropy \< .90 because poor class
    separability compromises interpretability of the results
5.  We do not consider solutions with minimum posterior classification
    probability \< .90 because poor class separability compromises
    interpretability of the results

```{r eval = FALSE, echo = TRUE}
# Get fit table fit
tab_fit <- table_fit(res_step)
# Select columns
tab_fit <- tab_fit[, c("Name", "Classes", "LL", "Parameters", "BIC", "Entropy", "prob_min", "n_min", "warning", "lmr_p")]
tab_fit
```

```{r tabfit, eval = TRUE, echo = FALSE, results = "asis"}
# Get fit table fit
tab_fit <- readRDS("appendices/lcga_fit.RData")
tab_fit <- tab_fit[, c("Name", "Classes", "LL", "Parameters", "BIC", "Entropy", "prob_min", "n_min", "warning", "lmr_p")]
names(tab_fit) <- c("Name", "Classes", "LL", "p", "BIC", "Ent.", "p_min", "n_min", "warn", "lmr_p")
papaja::apa_table(tab_fit, digits = 2, caption = "Fit of LCGA models")
```

@@

The first two LMR tests are significant, indicating that a 2- and
3-class solution were a significant improvement over a 1- and 2-class
solution, respectively. However, solutions with \>3 classes had entropy
and minimum posterior classification probability below the pre-specified
thresholds. Models with \>3 solutions also had fewer than five
observations per parameter. This suggests that the preferred model
should be selected from 1-3 classes.

@@

```{r plotscree, echo = TRUE, eval = FALSE}
plot(tab_fit, statistics = c("AIC", "BIC", "saBIC"))
```

```{r echo = FALSE, eval = run_everything}
p <- plot(tab_fit, statistics = c("AIC", "BIC", "saBIC"))
ggsave("appendices/lcga_plot_fit.png", p, width = 150, height = 120, units = "mm")
```

```{r echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/lcga_plot_fit.png")
```

Based on the aforementioned criteria, we selected a 3-class model for
further analyses. First, to prevent label switching, we re-order these
classes by the value of the intercept `i`. Then, we report the estimated
parameters.

```{r echo = TRUE, eval = FALSE}
res_final <- mx_switch_labels(res_step[[3]], param = "M[1,7]", decreasing = FALSE)
tab_res <- table_results(res_final, columns = NULL)
# Select rows and columns
tab_res <- tab_res[tab_res$Category %in% c("Means", "Variances"), c("Category", "lhs", "est", "se", "pval", "confint", "name")]
tab_res
```

```{r echo = FALSE, eval = run_everything, results='asis'}
res_final <- mx_switch_labels(res_step[[3]], param = "M[1,7]", decreasing = FALSE)
tab_res <- table_results(res_final, columns = NULL)
write.csv(tab_res, "lcga_tab_res.csv", row.names = FALSE)
```

```{r tabres, echo=FALSE, eval = TRUE, results='asis'}
tab_res <- read.csv("appendices/lcga_tab_res.csv", stringsAsFactors = FALSE)
class(tab_res) <- c("tidy_results", "data.frame")
tab_res <- tab_res[tab_res$Category %in% c("Means", "Variances"), c("Category", "lhs", "est", "se", "pval", "confint", "name")]
papaja::apa_table(tab_res, digits = 2, caption = "Results from 3-class LCGA model", longtable = TRUE)
```

@@

```{r params, echo = TRUE, eval = FALSE}
names(coef(res_final))
```

```{r echo = FALSE, eval = TRUE}
c("mix3.weights[1,2]", "mix3.weights[1,3]", "vscl1", "vscl2", 
"vscl3", "vscl4", "vscl5", "vscl6", "class1.M[1,7]", "class1.M[1,8]", 
"class1.M[1,9]", "class2.M[1,7]", "class2.M[1,8]", "class2.M[1,9]", 
"class3.M[1,7]", "class3.M[1,8]", "class3.M[1,9]")
```

@@

```{r echo = TRUE, eval = FALSE}
wald_tests <- wald_test(res_final, 
                   "
                   class1.M[1,7] = class2.M[1,7]&
                   class1.M[1,7] = class3.M[1,7];
                   class1.M[1,8] = class2.M[1,8]&
                   class1.M[1,8] = class3.M[1,8];
                   class1.M[1,9] = class2.M[1,9]&
                   class1.M[1,9] = class3.M[1,9]")
# Rename the hypothesis
wald_tests$Hypothesis <- c("Mean i", "Mean step", "Mean slope")
papaja::apa_table(wald_tests, digits = 2, caption = "Wald tests")
```

```{r echo = FALSE, eval = run_everything}
wald_tests <- wald_test(res_final, 
                   "class1.M[1,7] = class2.M[1,7]&class1.M[1,7] = class3.M[1,7];class1.M[1,8] = class2.M[1,8]&class1.M[1,8] = class3.M[1,8];class1.M[1,9] = class2.M[1,9]&class1.M[1,9] = class3.M[1,9]")
# Rename the hypothesis
wald_tests$Hypothesis <- c("Mean i", "Mean step", "Mean slope")
write.csv(wald_tests, "lcga_wald_tests.csv", row.names = FALSE)
```

```{r waldtests, echo = FALSE, eval = TRUE, results='asis'}
wald_tests <- read.csv("appendices/lcga_wald_tests.csv", stringsAsFactors = FALSE)
class(wald_tests) <- c("wald_test", "data.frame")
papaja::apa_table(wald_tests, digits = 2, caption = "Wald tests")
```

@@

```{r makelcgaplot, echo = TRUE, eval = FALSE}
p <- plot_growth(res_step[[3]], rawdata = TRUE, alpha_range = c(0, .05))
# Add Y-axis breaks in original scale
brks <- seq(0, 1, length.out = 5)
labs <- round(invbc(scales::rescale(brks, from = c(0, 1), to = rng_bc), lambda))
p <- p + scale_y_continuous(breaks = seq(0, 1, length.out = 5), labels = labs) + ylab("SCL (rescaled from Box-Cox)")
p
```

```{r echo = FALSE, eval = run_everything}
p <- plot_growth(res_step[[3]], rawdata = TRUE, alpha_range = c(0, .05))
# Add Y-axis breaks in original scale
brks <- seq(0, 1, length.out = 5)
labs <- round(invbc(scales::rescale(brks, from = c(0, 1), to = rng_bc), lambda))
p <- p + scale_y_continuous(breaks = seq(0, 1, length.out = 5), labels = labs) + ylab("SCL (rescaled from Box-Cox)")
ggsave("appendices/plot_traj.png", p, width = 150, height = 120, units = "mm")
```

```{r echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/plot_traj.png")
```

>>>>

---
title             : "Appendix C: Latent Class Growth Analysis"
shorttitle        : "BEST PRACTICES LATENT CLASS ANALYSIS"

bibliography      : "r-references.bib"

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r echo = TRUE, eval = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
ggplot(df_plot, aes(x = scl)) +
  geom_density() +
  facet_wrap(~time) + theme_bw()
```
```{r, eval = run_everything, echo = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
p = ggplot(df_plot, aes(x = scl)) +
  geom_density() +
  facet_wrap(~time) + theme_bw()
ggsave("appendices/plot_dist.png", p, width = 150, height = 120, units = "mm")
```
```{r, echo = FALSE, out.width="50%", eval = pkgdown}
knitr::include_graphics("appendices/plot_dist.png")
```

@@

```{r, eval = FALSE, echo = TRUE}
# Make plot data
df_plot <- do.call(rbind, lapply(c("scl", "log", "sqrt", "qrt", "boxcox"), function(n){
  data.frame(df_scores[c("time", "id")],
             Value = df_scores[[n]],
             Transformation = n)
}))
# Plot
ggplot(df_plot, aes(x = Value, colour = Transformation)) +
  geom_density() +
  facet_wrap(~time) +
  scale_y_sqrt() +
  xlab("scl (rescaled to 0-1)") +
  theme_bw()
```
```{r, eval = run_everything, echo = FALSE}
df_plot <- reshape(df, direction = "long", varying = names(df))
df_scores <- df_plot
# Store original range of SCL
rng_scl <- range(df_scores$scl)
# Log-transform
df_scores$log <- scales::rescale(log(df_scores$scl), to = c(0, 1))
# Square root transform
df_scores$sqrt <- scales::rescale(sqrt(df_scores$scl), to = c(0, 1))
# Cube root transform
df_scores$qrt <- scales::rescale(df_scores$scl^.33, to = c(0, 1))
# Reciprocal transform
df_scores$reciprocal <- scales::rescale(1/df_scores$scl, to = c(0, 1))
# Define function for Box-Cox transformation
bc <- function(x, lambda){
  (((x ^ lambda) - 1) / lambda)
}
# Inverse Box-Cox transformation
invbc <- function(x, lambda){
  ((x*lambda)+1)^(1/lambda)
}
# Box-Cox transform
b <- MASS::boxcox(lm(df_scores$scl ~ 1), plotit = FALSE)
lambda <- b$x[which.max(b$y)]
df_scores$boxcox <- bc(df_scores$scl, lambda)
# Store range of Box-Cox transformed data
rng_bc <- range(df_scores$boxcox)
df_scores$boxcox <- scales::rescale(df_scores$boxcox, to = c(0, 1))
# Rescale SCL
df_scores$scl <- scales::rescale(df_scores$scl, to = c(0, 1))

df_plot <- do.call(rbind, lapply(c("scl", "log", "sqrt", "qrt", "boxcox"), function(n){
  data.frame(df_scores[c("time", "id")],
             Value = df_scores[[n]],
             Transformation = n)
}))
# Plot
p <- ggplot(df_plot, aes(x = Value, colour = Transformation)) +
  geom_density() +
  facet_wrap(~time) +
  scale_y_sqrt() +
  xlab("scl (rescaled to 0-1)") +
  theme_bw()
ggsave("appendices/plot_trans.png", p, width = 150, height = 120, units = "mm")
```
```{r, echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/plot_trans.png")
```

@@

@@

```{r echo = FALSE, eval = run_everything}
set.seed(27796)
dat[["id"]] <- NULL
res_step <- mx_growth_mixture(
  model =
"i =~ 1*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6
step =~ 0*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6
s =~ 0*scl1 + 0*scl2 + 1*scl3 +2*scl4 +3*scl5 +4*scl6
scl1 ~~ vscl1*scl1
scl2 ~~ vscl2*scl2
scl3 ~~ vscl3*scl3
scl4 ~~ vscl4*scl4
scl5 ~~ vscl5*scl5
scl6 ~~ vscl6*scl6
i ~~ 0*i
step ~~ 0*step
s ~~ 0*s
i ~~ 0*s
i ~~ 0*step
s ~~ 0*step", classes = 1:5,
  data = dat)
# Additional iterations because of
# convergence problems for model 1:
res_step[[1]] <- mxTryHardWideSearch(res_step[[1]], extraTries = 50)
saveRDS(res_step, "appendices/res_step.RData")
fit <- table_fit(res_step)
saveRDS(fit, "appendices/lcga_fit.RData")
```
```{r, echo = FALSE, eval = FALSE}
res_step <- readRDS("appendices/res_step.RData")
```

Note that the first model showed convergence problems, throwing the error:
*The model does not satisfy the 
first-order optimality conditions to
the required accuracy, and no improved
point for the merit function could be
found during the final linesearch.*
To address this problem, we performed
additional iterations to  
find a better solution, using `OpenMx::mxTryHardWideSearch()`.
This also illustrates that `tidySEM` mixture models inherit from `OpenMx`'s `MxModel`,
and thus, different `OpenMx` functions can be used to act on models specified via `tidySEM`.

@@

1. We do not consider classes with, on average, fewer than 5 participants per parameter in a class due to potential local underidentification
1. Lower values for information criteria (AIC, BIC, saBIC) indicate better fit
1. Significant Lo-Mendell-Rubin LRT test indicates better fit for $k$ vs $k-1$ classes
1. We do not consider solutions with entropy < .90 because poor class separability compromises interpretability of the results
1. We do not consider solutions with minimum posterior classification probability < .90 because poor class separability compromises interpretability of the results

```{r eval = FALSE, echo = TRUE}
# Get fit table fit
tab_fit <- table_fit(res_step)
# Select columns
tab_fit <- tab_fit[, c("Name", "Classes", "LL", "Parameters", "BIC", "Entropy", "prob_min", "n_min", "warning", "lmr_p")]
tab_fit
```
```{r tabfit, eval = TRUE, echo = FALSE, results = "asis"}
# Get fit table fit
tab_fit <- readRDS("appendices/lcga_fit.RData")
tab_fit <- tab_fit[, c("Name", "Classes", "LL", "Parameters", "BIC", "Entropy", "prob_min", "n_min", "warning", "lmr_p")]
names(tab_fit) <- c("Name", "Classes", "LL", "p", "BIC", "Ent.", "p_min", "n_min", "warn", "lmr_p")
papaja::apa_table(tab_fit, digits = 2, caption = "Fit of LCGA models")
```

@@

The first two LMR tests are significant,
indicating that a 2- and 3-class solution were a significant improvement over a 1- and 2-class solution, respectively.
However, solutions with >3 classes had entropy and minimum posterior classification probability below the pre-specified thresholds.
Models with >3 solutions also had fewer than five observations per parameter.
This suggests that the preferred model should be selected from 1-3 classes.

@@

```{r plotscree, echo = TRUE, eval = FALSE}
plot(tab_fit, statistics = c("AIC", "BIC", "saBIC"))
```
```{r echo = FALSE, eval = run_everything}
p <- plot(tab_fit, statistics = c("AIC", "BIC", "saBIC"))
ggsave("appendices/lcga_plot_fit.png", p, width = 150, height = 120, units = "mm")
```
```{r echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/lcga_plot_fit.png")
```

Based on the aforementioned criteria,
we selected a 3-class model for further analyses.
First, to prevent label switching,
we re-order these classes by the value of the intercept `i`.
Then, we report the estimated parameters.
```{r echo = TRUE, eval = FALSE}
res_final <- mx_switch_labels(res_step[[3]], param = "M[1,7]", decreasing = FALSE)
tab_res <- table_results(res_final, columns = NULL)
# Select rows and columns
tab_res <- tab_res[tab_res$Category %in% c("Means", "Variances"), c("Category", "lhs", "est", "se", "pval", "confint", "name")]
tab_res
```
```{r echo = FALSE, eval = run_everything, results='asis'}
res_final <- mx_switch_labels(res_step[[3]], param = "M[1,7]", decreasing = FALSE)
tab_res <- table_results(res_final, columns = NULL)
write.csv(tab_res, "lcga_tab_res.csv", row.names = FALSE)
```
```{r tabres, echo=FALSE, eval = TRUE, results='asis'}
tab_res <- read.csv("appendices/lcga_tab_res.csv", stringsAsFactors = FALSE)
class(tab_res) <- c("tidy_results", "data.frame")
tab_res <- tab_res[tab_res$Category %in% c("Means", "Variances"), c("Category", "lhs", "est", "se", "pval", "confint", "name")]
papaja::apa_table(tab_res, digits = 2, caption = "Results from 3-class LCGA model", longtable = TRUE)
```

@@

```{r params, echo = TRUE, eval = FALSE}
names(coef(res_final))
```
```{r echo = FALSE, eval = TRUE}
c("mix3.weights[1,2]", "mix3.weights[1,3]", "vscl1", "vscl2", 
"vscl3", "vscl4", "vscl5", "vscl6", "class1.M[1,7]", "class1.M[1,8]", 
"class1.M[1,9]", "class2.M[1,7]", "class2.M[1,8]", "class2.M[1,9]", 
"class3.M[1,7]", "class3.M[1,8]", "class3.M[1,9]")
```

@@

```{r echo = TRUE, eval = FALSE}
wald_tests <- wald_test(res_final, 
                   "
                   class1.M[1,7] = class2.M[1,7]&
                   class1.M[1,7] = class3.M[1,7];
                   class1.M[1,8] = class2.M[1,8]&
                   class1.M[1,8] = class3.M[1,8];
                   class1.M[1,9] = class2.M[1,9]&
                   class1.M[1,9] = class3.M[1,9]")
# Rename the hypothesis
wald_tests$Hypothesis <- c("Mean i", "Mean step", "Mean slope")
papaja::apa_table(wald_tests, digits = 2, caption = "Wald tests")
```
```{r echo = FALSE, eval = run_everything}
wald_tests <- wald_test(res_final, 
                   "class1.M[1,7] = class2.M[1,7]&class1.M[1,7] = class3.M[1,7];class1.M[1,8] = class2.M[1,8]&class1.M[1,8] = class3.M[1,8];class1.M[1,9] = class2.M[1,9]&class1.M[1,9] = class3.M[1,9]")
# Rename the hypothesis
wald_tests$Hypothesis <- c("Mean i", "Mean step", "Mean slope")
write.csv(wald_tests, "lcga_wald_tests.csv", row.names = FALSE)
```
```{r waldtests, echo = FALSE, eval = TRUE, results='asis'}
wald_tests <- read.csv("appendices/lcga_wald_tests.csv", stringsAsFactors = FALSE)
class(wald_tests) <- c("wald_test", "data.frame")
papaja::apa_table(wald_tests, digits = 2, caption = "Wald tests")
```

@@

```{r makelcgaplot, echo = TRUE, eval = FALSE}
p <- plot_growth(res_step[[3]], rawdata = TRUE, alpha_range = c(0, .05))
# Add Y-axis breaks in original scale
brks <- seq(0, 1, length.out = 5)
labs <- round(invbc(scales::rescale(brks, from = c(0, 1), to = rng_bc), lambda))
p <- p + scale_y_continuous(breaks = seq(0, 1, length.out = 5), labels = labs) + ylab("SCL (rescaled from Box-Cox)")
p
```
```{r echo = FALSE, eval = run_everything}
p <- plot_growth(res_step[[3]], rawdata = TRUE, alpha_range = c(0, .05))
# Add Y-axis breaks in original scale
brks <- seq(0, 1, length.out = 5)
labs <- round(invbc(scales::rescale(brks, from = c(0, 1), to = rng_bc), lambda))
p <- p + scale_y_continuous(breaks = seq(0, 1, length.out = 5), labels = labs) + ylab("SCL (rescaled from Box-Cox)")
ggsave("appendices/plot_traj.png", p, width = 150, height = 120, units = "mm")
```
```{r echo = FALSE, eval = pkgdown, out.width="50%"}
knitr::include_graphics("appendices/plot_traj.png")
```
